Approximation as Differentiation

### 2025-05-06 appendix/notes/auto-diff.tex
Tweak.

\noindent and again we can define a corresponding category $\Diff^*$ of such maps where composition of the
cotangent maps respects the backward chain rule, with in this case $\Diff^*$ equivalent to a full subcategory
of $\Fam(\FinVect^\op)$.

>>>>

\noindent and again define a corresponding category $\Diff^*$ (equivalent to a full subcategory of
$\Fam(\FinVect^\op)$) of such maps where composition of the cotangent maps respects the backward chain rule.

\todo{The reason we can't combine $\Diff$ and $\Diff^*$ into a single category, with morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n) \times (\RR^n \linearto \RR^m)$ is..?}

### 2025-05-06 appendix/notes/fam.tex
Tweak.

\begin{definition}
Then define $\Fam(-,\cat{C}): \Set^{\op} \to \Cat$ to be the indexed category which sends any set $I$ to
$\Fam(I,\cat{C})$ and any function $f: I \to J$ to the functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to
\Fam(I,\cat{C})$.
\end{definition}

>>>>

\begin{definition}
Define $\Fam(-,\cat{C}): \Set^{\op} \to \Cat$ to be the indexed category which sends any set $I$ to
$\Fam(I,\cat{C})$ and any function $f: I \to J$ to the functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to
\Fam(I,\cat{C})$.
\end{definition}
